Dynein project log

### 2016-09-05 thesis_stuff/thesis_stuff.tex
Add citations to thesis_stuff.tex

>>>>

\section{Citations}
Cianfrocco, M*., DeSantis, M*., Leschziner, A., Reck-Peterson, S. ``Mechanism and Regulation of Cytoplasmic Dynein'' \textit{Annu. Rev. Cell. Dev. Biol.} 2015: 31:83-108.\\

Qiu, W., Derr, N., Goodman, B., Villa, E., Wu, D., Shih, W., Reck-Pterson, S. ``Dynein achieves processive motion using both stochastic and coordinated stepping.'' \textit{Nature Structural & Molecular Biology}. 2012, 19:193-200.\\
